GVN-Hoist: Hoisting Computations from Branches

### 2016-08-14 hoist.tex
move example

\subsection{Illustrative Example}
In the case when more than one computation from the same basic block
shows up as redundant.

e.g.
\begin{verbatim}
BB1
load a;
....
store .;
....
load a;

BB2
load a

BB0 -> BB1
BB0 -> BB2
\end{verbatim}

In this case both the loads from BB1 will show up as redundant
(according to the current algorithm), but the complete hoising will
fail as the second load in BB1 is not safe to hoist. By following the
bottom-up approach, the sorted list of BBs will appear like this:

{ BB1, BB2(first load), BB2(second load) }

Now we will start evaluating the safety of BB1-l1 and BB2-l2 which
will pass, then BB12-l1 and BB2-l2 will fail.  So we can revert back
to BB12-l1 and hoist them to BB0. Doing the top down approach and
finding the partial set to hoist instructions partially would result
in a combinatorial explosion.

@@

\subsection{Exposing more ILP}
Code hoisting can also reduce the critical path length of execution in out of
order machines. As more instructios are available at the hoisting point, the
hardware has more instructions to reorder. Following example illustrates how
hoisting can improve performance by exposing more ILP.

>>>>

\subsection{Illustrative Example}
Code hoisting can also reduce the critical path length of execution in out of
order machines. As more instructios are available at the hoisting point, the
hardware has more instructions to reorder. Following example illustrates how
hoisting can improve performance by exposing more ILP.

@@
